---
title: "Plots Equotip Leeb rebound C hardness measurements"
author: David Nora, Joao Marreiros, Walter Gneisinger
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_knit$set(comment = NA, message = FALSE, indent = "", error = TRUE)

```

---

# Content
This script reads and plots the data from the  Leeb Rebound hardness.  Hardness was measured on each rock using the device Equotip 550 Leeb Impact device C (HLC). For details on the methods and data acquisition, please visit the Materials and Methods section of the paper. 

The knit directory for this script is the project directory.

---
# Load packages

```{r}

library(tidyverse)
library(AICcmodavg)
library(ggplot2)
library(utils)
library(qwraps2)
library(kableExtra)
library(doBy)
library(ggpubr)

```

------------------------------------------------------------------------

# Read in original xlsx-file

```{r}
# List all CSV files in dir_in

harddata <- read_csv2("../rawdata/data.csv")

# A total of 10 measurements were taken on each rock sample, 4 raw materials, 6 samples each

```

# Organise data

```{r}
# organising and summarising data by Sample ID
longdata <- harddata %>%
  gather("M1", "M2","M3", "M4", "M5","M6","M7", "M8", "M9", "M10", key = Measurment, value = HLC)

# Show new format
longdata

# Save the new format
write_csv(longdata, "../deriveddata/longdata.csv")

```

# Descriptive stats

```{r}
# descriptive statistics
# summarise data by each sample

# summarise by "Raw Material" but keep other columns

hlcstatsmaterial <- longdata %>% group_by(rawmaterial) %>%
      summarise(
      hlccount = n(),
      hlcmax = max(HLC, na.rm = TRUE),
      hlcmin = min (HLC, na.rm = TRUE),
      hlcmean = mean(HLC, na.rm = TRUE),
      hlcsd = sd(HLC, na.rm = TRUE),
      hlcmedian = median(HLC, na.rm = TRUE),
  ) 

# summarise by "Sample/ID" but keep other columns

hlcstatssample <- longdata %>% group_by(ID, rawmaterial) %>%
      summarise(
      vlcount = n(),
      vlmax = max(HLC, na.rm = TRUE),
      vlmin = min (HLC, na.rm = TRUE),
      vlmean = mean(HLC, na.rm = TRUE),
      vlsd = sd(HLC, na.rm = TRUE),
      vlmedian = median(HLC, na.rm = TRUE),
   )

# View results
hlcstatsmaterial
hlcstatssample

# Same results
write_csv(hlcstatsmaterial, "../stats/stats_hardness_maerial.csv")
write_csv(hlcstatssample, "../stats/stats_hardness_sample.csv")

```

# Reorder raw material categories
```{r}

longdata$rawmaterial <- factor(longdata$rawmaterial, levels=c('flint', 'obsidian', 'dacite', 'quartzite'))

```

# Plot data (one numerical continuious variable - HLC)

```{r}
# Boxplot

bp <- ggplot (longdata, aes(rawmaterial, HLC, color = grain)) + 
  geom_jitter(aes(shape = rawmaterial)) + 
  labs(x="Raw material", y="Leeb Rebound Hardness in HLC", title="", color="Category", shape="Raw material") +
  geom_boxplot()
             

print(bp)

ggsave("../plots/hardnessplot.png")

```

```{r}
# Density plot
dp <- ggplot (longdata, aes(x = HLC, color = grain, linetype = rawmaterial)) + 
             theme_classic() +
  scale_linetype_manual(values=c("twodash", "dotted", "solid", "longdash")) +
             geom_density() + labs(x="Leeb Rebound Hardness in HLC", y="Density", title="")

print(dp)

ggsave("../plots/densityplot.png")

```

# sessionInfo() and RStudio version

```{r}
sessionInfo()

```
