---
title: "Plots 3D data"
author: David Nora, Joao Marreiros, Walter Gneisinger
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r Knitr Options, include=FALSE}
knitr::opts_chunk$set(comment=NA, message=FALSE, indent="", error=TRUE)

```

---

# Content
This script reads and plots the data from the 3D volume loss, which was calculated using CloudCompare cloud-to-mesh distance tool. 
The knit directory for this script is the project directory.

---

# Load packages
```{r}
library(R.utils)
library(ggplot2)
library(tools)
library(tidyverse)
library(doBy)
library(ggrepel)

```


---

# Load data db 
```{r}

# Cloud-to-mesh calculations (before and after) for each sample were compiled in a single .csv file. File is formatted as exported from CloudCompare. We add a new column "Cycles".
# Import dataset
imp_data <- read_csv2("../rawdata/3dedge.csv")
str(imp_data)

```

# Reorder raw material categories
```{r}

imp_data$raw.material <- factor(imp_data$raw.material, levels=c('flint', 'obsidian', 'dacite', 'quartzite'))

```


# organise and sort data

```{r}

# organise and represent data differently so that mean and sd can be calculated
# now it shows how many times a value (distance) is represented by each class (sample segmentation)

data.expanded <- imp_data[rep(row.names(imp_data), imp_data$value), 1:7]

write_csv(data.expanded, "../deriveddata/dataexpanded.csv")

```

# Summarize data

```{r}

# Calculate distance (edge reduction) means between raw materials, samples and cycles

## exclude 0-500 cycles, which corresponds to the starting and ending point
data.expanded.cycles <- data.expanded %>% filter(!cycle == "0-500")

## Calculate

volumelossstats <- data.expanded.cycles %>% group_by(ID, grain, raw.material, cycle) %>%
      summarise(
      vlcount = n(),
      vlmax = max(value, na.rm = TRUE),
      vlmin = min (value, na.rm = TRUE),
      vlmean = mean(value, na.rm = TRUE),
      vlsd = sd(value, na.rm = TRUE),
      vlmedian = median(value, na.rm = TRUE),
   )

write_csv(volumelossstats, "../stats/volumelossstats.csv")

```

# Plot data organised by raw material and sample ID

```{r}

volumelossstats$raw.material <- factor(volumelossstats$raw.material, levels=c('flint', 'obsidian', 'dacite', 'quartzite'))

volumelossstats$grain <- factor(volumelossstats$grain, levels=c("fine", "coarse"))

# Plot data (edge reduction) organised by raw material and cycle (sequential experiment: 0-125, 125-250, 250-500)

## Plot selected data (cycles)

edre <- ggplot(data = volumelossstats, aes(x = cycle, y = vlmax)) + 
  geom_boxplot(aes(colour = grain, linetype = raw.material), outlier.colour = "", outlier.shape = 1) +
  scale_linetype_manual(values=c("twodash", "dotted", "solid", "longdash")) +
  geom_jitter(aes(colour = grain), alpha=0.2, position=position_jitter(w=0.1,h=0.1)) +
  labs(y = "Edge wear (Ew)", x = "Cycles", colour = "Category", linetype = "Raw material")

ggsave("../plots/cycles_rawmaterial.png")

print(edre)

```

---

# sessionInfo() and RStudio version

```{r}
sessionInfo()

```

---

END OF SCRIPT
